Text Is All You Need

### 2023-05-10 docs/hes_final/presentation.qmd
Transformer Slide Edits

- Our third approach used a pair of encoder-only transformers
- the “encoder” and the “classifier”.
- The encoder was used to reduce the dimensionality of the embedding corpus by analyzing a subset of article embeddings and returning a single vector of substantially reduced size.
- Analogous to the role of a convolutional layer in a CNN. 
- The classifier could then be used to make final predictions on the resulting, distilled dataset.

>>>>

- Our third approach used a pair of encoder-only transformers
- the “encoder” and the “classifier”.
- The encoder was used to distil the embedding corpus by analyzing a subset of article corpus and reducing it's dimensionality.
- The classifier could then be used to make final predictions on the resulting, distilled dataset.
